Final assignment presentation

### 2022-12-01 summary_final_assingment.Rmd
edit_opening

-   between 2016 and 2022 there have been major shifts in terms of majorities in the US congress:

    -   in 2016, both chambers were hold by Republicans

    -   in 2018, the Democrats gained a majority in Congress

    -   in 2020 the Democrats gained Congress and Senate

@@

We scraped our data from: https://data.gov/developers/apis/index.html

@@

## Density of cosponsors
```{r}
ggplot(df, aes(x = cosponsor_D_perc)) + 
  geom_histogram(aes(y=..density..), colour="black", fill="white") +
  geom_density(alpha=.1, fill="blue") +
  labs(title="Density of bill cosposor party",
       x ="Cosponsor party composition", y = "Density", 
       caption = "Numbers represent proportion of cosponsors from Democratic party, 
       so 0.0 represents bills that were fully Republican and 1.0 represents 
       bills that were fully Democrat.") +
  theme_minimal()
```

@@

## Creatung a dfm from the corpus
```{r }
dfmat <- corp %>%
  tokens(remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE) %>%
  tokens_remove(patter = stopwords("en")) %>%
  tokens_replace(pattern = lexicon::hash_lemmas$token, replacement = lexicon::hash_lemmas$lemma) %>%
  tokens_wordstem() %>%
  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "use", "author","fund","provid","program","requir","divis","titl","appropri","specifi")) %>%
  dfm()

@@

## Conclusion
- In general the legilsation appears quite similar, with exceptions limited to specific policy areas and topics
- Democratic and Republican cooperation across the different congress sessions is highly dependent on the policy area and topic of the bill
- There are some key actors that enable working across the aisle and are known for bipartisan collaboration

>>>>

-   Between 2017 and 2022 there have been major shifts in terms of majorities in the US congress:

    -   In the 115th Congress (Jan 2017 - Dec 2018), both chambers were hold by Republicans

    -   In the 116th Congress (Jan 2019 - Dec 2020), the Democrats gained a majority in Congress, the Republicans remained in the majority in the Senate

    -   In the 117th Congress (Jan 2021 - Dec 2022), the Democrats gained Congress and the Senate

@@

We scraped our data from: <https://data.gov/developers/apis/index.html>

@@

## Density of cosponsors

```{r}
ggplot(df, aes(x = cosponsor_D_perc)) + 
  geom_histogram(aes(y=..density..), colour="black", fill="white") +
  geom_density(alpha=.1, fill="blue") +
  labs(title="Density of bill cosposor party",
       x ="Cosponsor party composition", y = "Density", 
       caption = "Numbers represent proportion of cosponsors from Democratic party, 
       so 0.0 represents bills that were fully Republican and 1.0 represents 
       bills that were fully Democrat.") +
  theme_minimal()
```

@@

## Creatung a dfm from the corpus

```{r }
dfmat <- corp %>%
  tokens(remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE) %>%
  tokens_remove(patter = stopwords("en")) %>%
  tokens_replace(pattern = lexicon::hash_lemmas$token, replacement = lexicon::hash_lemmas$lemma) %>%
  tokens_wordstem() %>%
  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "use", "author","fund","provid","program","requir","divis","titl","appropri","specifi")) %>%
  dfm()

@@

## Conclusion

-   In general the legilsation appears quite similar, with exceptions limited to specific policy areas and topics
-   Democratic and Republican cooperation across the different congress sessions is highly dependent on the policy area and topic of the bill
-   There are some key actors that enable working across the aisle and are known for bipartisan collaboration
